\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Darshan Shirodkar} & Email: \href{mailto:darshanshirodkar@gmail.com}{darshanshirodkar@gmail.com}\\
  Toronto, ON & Mobile: {+1-437-237-6027} \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Shopify}{Toronto, ON, Canada}
      {Senior Data Scientist}{July 2022 - Present}
      \begin{itemize}
     \item I have had the opportunity to dive deep into Shopify's marketing product ecosystem, 
     collaborating with the product team to uncover insights on adoption, usage, and performance
     of various marketing tools. 
     \item My work involved designing and executing A/B experiments to validate hypotheses, 
     as well as generating insights to inform product direction. 
     \item I also worked on building and migrating data pipelines in PySpark and DBT to deliver essential analytical reports to Shopify's merchants.
      \end{itemize}
    \resumeSubheading
      {Zendrive}{Bengaluru, India}
      {Senior Data Scientist}{Jan 2021 - Jun 2022}
	\begin{itemize}
      \item Zendrive is a telematics company that helps insurance companies to provide usage based and driving behaviour based insurance to customers. 
     \item I worked as the lead data scientist on the Public Transport Detection team. We developed algorithms based on map-matching and vehicular dynamics to classify
      trips as ``car drive" vs ``public transit".
\end{itemize}
    \resumeSubheading
      {Microsoft}{Bengaluru, India}
      {Senior Data Scientist}{Dec 2018 - Jan 2021}
\begin{itemize}
\item I was part of the Bing Search Sponsored Ads team. We worked on optimization of ranking, allocation and pricing of sponsored search ads for all non-US markets.
\item A key part of my work included building a real-time algorithm for ad layout optimization using reinforcement learning. 
\end{itemize}
 \resumeSubheading
      {Precision Wellness}{San Francisco, CA}
      {Data Scientist - Consultant}{Feb 2018 - Nov 2018}
\begin{itemize}
\item My main contribution was to help identify and build a statistical model for
        predicting risk of cardiovascular disease based on various risk factors, and in scaling the algorithm implementation to millions of patient records using Pyspark.
\end{itemize}
\resumeSubheading
	{Adobe}{Bengaluru, India}
	{Data Science Manager}{Sep 2015 - Oct 2017}
\begin{itemize}
	\item I managed a small team of data scientists who focused on Adobe Media Optimizer, a search and display ad bidder. 
    \item My team worked on real-time estimation and adaptive control algorithms for our display ad bidder 
    and created a Python simulation environment to test various real-time bidding strategies for online auctions. 
\end{itemize}

\resumeSubheading
	{Pubmatic}{Pune, India}
	{Data Scientist}{June 2013 - Sep 2015}
\begin{itemize}
	\item As a member of the horizontal machine learning team, I tackled a variety of challenges, 
    often serving as a technical lead on revenue and infrastructure optimization problems. 
    \item One of my main contributions was to build a classification model to filter out low-quality ad opportunities from billions of ad requests
    that reduced infrastructure usage by 12\%.
\end{itemize}

\resumeSubheading
	{TCS Innovation Lab}{Pune, India}
	{Research Engineer}{Nov 2011 - Jun 2013}
\begin{itemize}
	\item I applied my skills in diverse areas, from quantitative finance to human resources. 
    \item I developed simulations in R to demonstrate the efficiency of Multi-level Monte Carlo techniques for pricing financial options. 
    \item Collaborating with the HR department, I also worked on mining employee data to identify high attrition groups within the company.   
\end{itemize}

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Illinois at Urbana-Champaign}{Urbana, IL}
      {Master of Science in Applied Mathematics; GPA: 3.96}{2009 -- 2011}
    \resumeSubheading
      {Indian Institute of Science}{Bengaluru, India}
      {Master of Engineering in Signal Processing; GPA: 7.4/8}{2006 -- 2008}
    \resumeSubheading
      {KJ somaiya College of Engineering}{Mumbai, India}
      {Bachelor of Engineering in Electronics}{2002 -- 2006}
  \resumeSubHeadingListEnd


\section{Publications}
  \resumeSubHeadingListStart
    \item{
    D. Shirodkar and S. Meyn, "Quasi stochastic approximation," Proceedings of the 2011 American Control Conference, San Francisco, CA, USA, 2011, pp. 2429-2435, doi: 10.1109/ACC.2011.5991485.
    }
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
%\section{Projects}
%  \resumeSubHeadingListStart
%    \resumeSubItem{QuantSoftware Toolkit}
%      {Open source Python library for financial data analysis and machine learning for finance.}
%    \resumeSubItem{GitHub Visualization}
%      {Data visualization of Git log data using D3 to analyze project trends over time.}
%    \resumeSubItem{Recommendation System}
%      {Music and movie recommender systems using collaborative filtering on public datasets.}
%    \resumeSubItem{Mac Setup}
%      {Book that gives step-by-step instructions on setting up developer environment on macOS.}
%  \resumeSubHeadingListEnd


%--------SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python, SQL}
   \item
      \textbf{Tools \& Technologies}{: Pyspark, Hadoop, Google Cloud Services, Bigquery, Looker Studio}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
